LAGOS lake depth

### 2020-11-10 figures/01_geometry.Rmd
prototype Figure 2 best-fit lines, #20

gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts

@@

gg_slope_base <- ggplot(data = test) + 
  geom_point(aes(slope_mean, inlake_slope.y), size = 1) +
  geom_smooth(aes(slope_mean, inlake_slope.y), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
  alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.03, label = "R^2 == 0.17",
                                parse = TRUE, size = text_size) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts

>>>>

gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
  annotate("text", x = 2100, y = 150, 
           label = get_formula(
             lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))), 
           size = text_size) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts

@@

gg_slope_base <- ggplot(data = test) + 
  geom_point(aes(slope_mean, inlake_slope.y), size = 1) +
  geom_smooth(aes(slope_mean, inlake_slope.y), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
  alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.03, label = "R^2 == 0.17",
                                parse = TRUE, size = text_size) +
  annotate("text", x = 0.34, y = 0.01, 
           label = get_formula(
             lm(inlake_slope.y ~ slope_mean, data = test)), 
           size = text_size) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts
